Figure 4. & 5. DGE's and Enrichment

### 2022-02-24 reports/manuscript/Figure2.Rmd
Tweaking plot sizes and output

---
title: "Figure 2. Bacterial Communities and Function"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")
metadata <- read.csv2("../../../results/metadata_integration.csv",row.names = 1, stringsAsFactors = F)
sample_use <- metadata$ID

SNN_bacteria <- read.csv("../../../results/bacteria_SNN_graph.csv",row.names = 1)
bac_communities <- as.matrix(read.csv2("../../../results/bacterial_communities.csv",row.names = 1))[,1]

group_annotation <- factor(setNames(metadata$Luminal_gr,metadata$ID))
gr <- "Luminal"

picrust_data <- read.table("../../../data/pred_metagenome_unstrat.tsv",header = T,row.names = 1)
picrust_KO_seq <- read.table("../../../data/KO_predicted.tsv",header = T,row.names = 1)
picrust_taxa <- read.table("../../../data/SeqID_to_taxa.csv",header = T,row.names = 1,sep = ",")

@@

### B
###################################
# WET SMEAR BACTERIAL VALIDATION #
###################################
par(mar=c(1,5,4,1)) #b,l,t,r
x <- datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]]
xL <- rowsum(x , grepl("L.",rownames(x)) )[2,] / sum(grepl("L.",rownames(x)))
xM <- rowsum(x , grepl("Mobiluncus",rownames(x)) )[2,] / sum(grepl("Mobiluncus",rownames(x)))
xG <- rowsum(x , grepl("Gardnerella",rownames(x)) )[2,] / sum(grepl("Gardnerella",rownames(x)))

@@

ko_names <- readLines('../../../data/ko_info.tsv')
ko_names <- strsplit(ko_names,"\t")
ko_names <- setNames(unlist(lapply(ko_names,function(x){x[2]})), unlist(lapply(ko_names,function(x){x[1]})))
ko_names <- sub(" [[].*","",ko_names)
ko_names <- sub(".*; ","",ko_names)

@@

source("../enrichment_function.R")
gmt_list <- fgsea::gmtPathways("../../../data/KEGG_pathways_to_KO.tsv")
kegg_names <- read.delim('../../../data/KEGG_pathways_info.tsv',header = F)
names(gmt_list) <- kegg_names [ match ( names(gmt_list), as.character(kegg_names[,1]) ) , 2 ]
gmt_list <- lapply(gmt_list , function(x){
  na.omit(ko_names[x])
})
res_list <- lapply( unique( gene_module[h$order] ),function(x){
  temp <- compute_enrichment(genes = names(gene_module)[gene_module==x],
                            gmt_list = gmt_list,
                            min_terms_pathway = 10,
                            max_terms_pathway = 300,
                            min_overlap = 3,
                            sort_by_pvalue = T)
  temp <- temp[!grepl("REGULATION",rownames(temp)),]
  return(temp)
} )
res <- map(res_list, ~rownames_to_column(.x, var = "Terms")) %>% 
    set_names(., paste0("module_",  seq_along(res_list)))

@@

pages <- list(list("Across"=top), res) %>% flatten()
write.xlsx(pages, file=paste0("./Suppl.Tbl/","Suppl.Tbl.02",".xlsx"))
```

>>>>

---
title: "Figure 2. Bacterial Communities and Function"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

#########
# PATHS #
#########
result_dir <- "./Suppl.Tbl/"
if( isFALSE(dir.exists(result_dir)) ) { dir.create(result_dir,recursive = TRUE) }

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
metadata <- read.csv("../../data/metadata.csv",row.names = 1, stringsAsFactors = F)
sample_use <- metadata$ID
group_annotation <- factor(setNames(metadata$Luminal_gr,metadata$ID))
gr <- "Luminal"

SNN_bacteria <- read.csv("../../results/04_clustering_output/bacteria_SNN_graph.csv",row.names = 1)
bac_communities <- as.matrix(read.csv("../../results/04_clustering_output/bacterial_communities.csv",row.names = 2))[,2]

picrust_data <- read.table("../../results/05_picrust_output/out_2021-01-20/KO_metagenome_out/pred_metagenome_unstrat.tsv", header = T,row.names = 1)
ko_names <- readLines('../../resources/picrust_data/ko_info.tsv')
kegg_names <- read.delim('../../resources/picrust_data/KEGG_pathways_info.tsv',header = F)
gmt_list <- fgsea::gmtPathways("../../resources/picrust_data/KEGG_pathways_to_KO.tsv")
source("../../code/enrichment_function.R")

@@

### B
###################################
# WET SMEAR BACTERIAL VALIDATION #
###################################
par(mar=c(1,5,4,1)) #b,l,t,r
x <- datasets_all_samples[["ASV_Luminal_normalized"]]
xL <- rowsum(x , grepl("L.",rownames(x)) )[2,] / sum(grepl("L.",rownames(x)))
xM <- rowsum(x , grepl("Mobiluncus",rownames(x)) )[2,] / sum(grepl("Mobiluncus",rownames(x)))
xG <- rowsum(x , grepl("Gardnerella",rownames(x)) )[2,] / sum(grepl("Gardnerella",rownames(x)))

@@

ko_names <- strsplit(ko_names,"\t")
ko_names <- setNames(unlist(lapply(ko_names,function(x){x[2]})), unlist(lapply(ko_names,function(x){x[1]})))
ko_names <- sub(" [[].*","",ko_names)
ko_names <- sub(".*; ","",ko_names)

@@

names(gmt_list) <- kegg_names [ match ( names(gmt_list), as.character(kegg_names[,1]) ) , 2 ]
gmt_list <- lapply(gmt_list , function(x){
  na.omit(ko_names[x])
})
res_list <- lapply( unique( gene_module[h$order] ),function(x){
  temp <- compute_enrichment(genes = names(gene_module)[gene_module==x],
                            gmt_list = gmt_list,
                            min_terms_pathway = 10,
                            max_terms_pathway = 300,
                            min_overlap = 3,
                            sort_by_pvalue = T)
  temp <- temp[!grepl("REGULATION",rownames(temp)),]
  return(temp)
} )
res <- map(res_list, ~rownames_to_column(.x, var = "Terms")) %>% 
    set_names(., paste0("module_",  seq_along(res_list)))

@@

pages <- list(list("Across"=top), res) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,"Suppl.Tbl.02",".xlsx"))
```

### 2022-02-24 reports/manuscript/Figure4-5.Rmd
Tweaking plot sizes and output

---
title: "DGE's and Enrichment"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

@@

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")
metadata <- read.csv2("../../../results/metadata_integration.csv",row.names = 1, stringsAsFactors = F)
sample_use <- metadata$ID

gr_name <- c("Luminal", "Tissue")
out <- paste0("./Suppl.Tbl/")

@@

@@

  source("../enrichment_function.R")
  if(db == "GO"){
  gmt_list <- fgsea::gmtPathways("../../../supplementary_files/c5.bp.v6.2.symbols.gmt.txt")}else{
  gmt_list <- fgsea::gmtPathways("../../../supplementary_files/c2.cp.kegg.v6.2.symbols.gmt.txt")}
  res_list <- lapply( unique( gene_module[h$order] ),function(x){
    temp <- compute_enrichment(genes = names(gene_module)[gene_module==x],
                              gmt_list = gmt_list,
                              min_terms_pathway = 10,
                              max_terms_pathway = 300,
                              min_overlap = 3,
                              sort_by_pvalue = T)
    temp <- temp[!grepl("REGULATION",rownames(temp)),]
    return(temp)
  } )

@@

#########
# DEG's #
#########
# Replace missing values with average in sexwork_months column
m <- round(sum(metadata$sexwork_months, na.rm = T)/nrow(metadata))
metadata <- metadata %>%
  mutate(sexwork_months = ifelse(is.na(.$sexwork_months), m, .$sexwork_months))

dge_L <- edgR_dge.fun("Luminal_gr", confound=T)
dge_T <- edgR_dge.fun("Tissue_gr", confound=T)

@@

###############################
# PAIRWISE ENRICHMENT GO/KEGG #
###############################
source("../enrichment_function.R")
gmt_list_KEGG <- fgsea::gmtPathways("../../../supplementary_files/c2.cp.kegg.v6.2.symbols.gmt.txt")
gmt_list_GO <- fgsea::gmtPathways("../../../supplementary_files/c5.bp.v6.2.symbols.gmt.txt")

#info_logFC <- map(top_dfs[[1]], ~table(abs(.x$logFC) > 1))
#info_PValue <- map(top_dfs[[1]], ~table(.$PValue < 0.01))

@@

## GO enrichment 
pairwise_GO <- map_depth(t_split, 3, ~enrich_list(.x$Genes, gmt_list_GO)) %>%
  map_depth(., 2, ~bind_rows(.x, .id = "regulation")) 
## KEGG enrichment
pairwise_KEGG <- map_depth(t_split, 3, ~enrich_list(.x$Genes, gmt_list_KEGG)) %>%
  map_depth(., 2, ~bind_rows(.x, .id = "regulation"))

@@

```{r Suppl. Tbl. 4 & 8, include=FALSE}
# DEG's across and pairwise
pages <- list(list(Across=dge_L$top), pairwise=pairwise_dge_L$top) %>% flatten()
write.xlsx(pages, file=paste0(out,DEG_files[1]))

pages <- list(list(Across=dge_T$top), pairwise=pairwise_dge_T$top) %>% flatten()
write.xlsx(pages, file=paste0(out,DEG_files[2]))
```

@@

write.xlsx(df_across[[1]]$res, file=paste0(out,"Suppl.Tbl.05 Enrichment_Across_Luminal",".xlsx"))
write.xlsx(df_across[[2]]$res, file=paste0(out,"Suppl.Tbl.09 Enrichment_Across_Tissue",".xlsx"))

@@

write.xlsx(df_pairwise[[1]]$value, file=paste0(out,"Suppl.Tbl.06 Enrichment_Pairwise_Luminal",".xlsx"))
write.xlsx(df_pairwise[[2]]$value, file=paste0(out,"Suppl.Tbl.10 Enrichment_Pairwise_Tissue",".xlsx"))
```

```{r TF PPI Analysis function, include=FALSE}
TF_PPI_analysis.fun <- function(out, filename, gr_name, outfile) {
  # Get DEG's files and filter p-value < 0.01
  sheets <- excel_sheets(paste0(out, filename)) %>% set_names(.) %>% .[-c(1:2)]
  detables <- map(sheets, ~read_xlsx(paste0(out, filename), sheet = .x, col_names = TRUE)) %>%
    map(.,~mutate(.x, DE = ifelse(.x$PValue > dge_cutoff , 0, ifelse(.x$logFC < 0, -1, 1 )))) %>% 
    map(.,~filter(., .$PValue <= 0.01))

@@

        }else{if(length(save_f) == 0){save_f <- append(save_f, f_n)} }
      }
      l <- bind_rows(save_f, .id = "Regulation") %>%
        filter(Adjusted.P.value <= 0.05)
      l <- set_names(list(l), paste0(i))
      save_l <- append(save_l, l ) 
    } 
    write.xlsx(save_l, file=paste0(out, outfile), row.names=FALSE)
  }
```

```{r TF PPI Analysis, eval=FALSE, include=FALSE}
TF_PPI_analysis.fun(out, DEG_files[1], gr_name[1], enrichR_files[1]) # writes Suppl.Tbl.07
TF_PPI_analysis.fun(out, DEG_files[2], gr_name[2], enrichR_files[2]) # writes Suppl.Tbl.11
```

@@

    f_DOWN <- read_xlsx(paste0(out, file), sheet = x) %>% filter(Regulation == "down")
    f_UP <- read_xlsx(paste0(out, file), sheet = x) %>% filter(Regulation == "up")

@@

sheets <- excel_sheets(paste0(out, DEG_files[1])) %>% set_names(.) %>% .[-c(1:2)]
arrange_plots.fun(enrich_L, "Luminal_gr", "Luminal", sheets, "TF_PPI_enrichment", enrichR_files[1], Layout = l)

@@

```{r Figure 5, message=FALSE, warning=FALSE, echo=FALSE, fig.height=6}
# Layout
l <- list(mat = matrix(c(1,2,3,4,4,4,5,5,5,
                         1,2,3,4,4,4,5,5,5,
                         6,6,6,7,7,8,8,9,9,
                         10,10,10,11,11,12,12,13,13),
                nrow = 3,ncol = 9,byrow = T),
          widths = c(1.14,3.5,.36,2.5,2.5,2.5,2.5,2.5,2.5),
          heigth = c(1,1,1.5)
          )

sheets <- excel_sheets(paste0(out, DEG_files[2])) %>% set_names(.) %>% .[-c(1:2)]
arrange_plots.fun(enrich_T, "Tissue_gr", "Tissue", sheets, "TF_PPI_enrichment", enrichR_files[2], Layout = l)

@@

pages <- list(list("DEGs L2T2 vs L2T3"=t), df_across[[1]]$res) %>% flatten()
write.xlsx(pages, file=paste0(out,"Suppl.Tbl.12 L2T2_L2T3_DEGs_and_enrichment.xlsx")) 
```

## igraph network plot
```{r igraph network, echo=FALSE, warning=FALSE} 
# 1. Change the groups of interest by assigning condition_use
# 2. Change the number of genes to be included in the network by changing n
#    look at tempD_i and tempU_i to see how many genes was significant
# 3. Adjust the size of the gene nodes and text in the graph by changing; square, circle and txt

# combinations
sheets <- map(DEG_files, ~excel_sheets(paste0(out, .x))[-c(1:2)] ) %>%
  map(., ~set_names(.x))

@@

# Save all combination plots in one file
save_pdf.fun <- function(i, gr_name, comp){
  temp_i_name <- grep(i,list.files(paste0(out),full.names=F),value=T)
  p <- map(comp, ~read_xlsx(paste0(out, temp_i_name), sheet = .x))

@@

  par(mar = c(0, 0, .7, 0))  #bottom, left, top, right
  pdf(file = paste0(out, "Plots/", i, "_network_",".pdf", sep=""))
    p <- imap(obj_igraph,
         ~with(.x, 
                 plot.igraph(g, label=V(g), page = T,
                 main = paste0(str_replace(.y, "_", " ")," regulated genes"),
                 layout=layout_with_kk(g), vertex.label.color="black" ,
                 vertex.size=v_size, vertex.label.cex=txt, vertex.label.font=2, 
                 vertex.shape=v_shape, vertex.color=v_color, marigin = c(-1,-4,0,0),
                 vertex.frame.color="grey60", curved=F)

@@

# if(isFALSE(dir.exists(paste0(out,"Plots")))){dir.create(paste0("../",result.dir),recursive = TRUE)}
# save_pdf.fun("TF_PPI_Luminal", "Luminal", comp = sheets[[1]])
# save_pdf.fun("TF_PPI_Tissue", "Tissue", comp = sheets[[2]])

>>>>

---
title: "Figure 4. & 5. DGE's and Enrichment"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

@@

#########
# PATHS #
#########
result_dir <- "./Suppl.Tbl/"
if( isFALSE(dir.exists(result_dir)) ) { dir.create(result_dir,recursive = TRUE) }

@@

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
metadata <- read.csv("../../data/metadata.csv",row.names = 1, stringsAsFactors = F)
sample_use <- metadata$ID
gr_name <- c("Luminal", "Tissue")

source("../../code/enrichment_function.R")
GO_database <- fgsea::gmtPathways("../../resources/KEGG_GO_database/c5.bp.v6.2.symbols.gmt.txt")
KEGG_database <- fgsea::gmtPathways("../../resources/KEGG_GO_database/c2.cp.kegg.v6.2.symbols.gmt.txt")

@@

  if(db == "GO"){
  gmt_list <- GO_database}else{
  gmt_list <- KEGG_database}
  res_list <- lapply( unique( gene_module[h$order] ),function(x){
    temp <- compute_enrichment(genes = names(gene_module)[gene_module==x],
                              gmt_list = gmt_list,
                              min_terms_pathway = 10,
                              max_terms_pathway = 300,
                              min_overlap = 3,
                              sort_by_pvalue = T)
    temp <- temp[!grepl("REGULATION",rownames(temp)),]
    return(temp)
  } )

@@

#########
# DEG's #
#########
dge_L <- edgR_dge.fun("Luminal_gr", confound=T)
dge_T <- edgR_dge.fun("Tissue_gr", confound=T)

@@

###############################
# PAIRWISE ENRICHMENT GO/KEGG #
###############################
#info_logFC <- map(top_dfs[[1]], ~table(abs(.x$logFC) > 1))
#info_PValue <- map(top_dfs[[1]], ~table(.$PValue < 0.01))

@@

## GO enrichment 
pairwise_GO <- map_depth(t_split, 3, ~enrich_list(.x$Genes, GO_database)) %>%
  map_depth(., 2, ~bind_rows(.x, .id = "regulation")) 
## KEGG enrichment
pairwise_KEGG <- map_depth(t_split, 3, ~enrich_list(.x$Genes, KEGG_database)) %>%
  map_depth(., 2, ~bind_rows(.x, .id = "regulation"))

@@

```{r Suppl. Tbl. 4 & 8, include=FALSE}
# DEG's across and pairwise
pages <- list(list(Across=dge_L$top), pairwise=pairwise_dge_L$top) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[1]))

pages <- list(list(Across=dge_T$top), pairwise=pairwise_dge_T$top) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,DEG_files[2]))
```

@@

write.xlsx(df_across[[1]]$res, file=paste0(result_dir,"Suppl.Tbl.05 Enrichment_Across_Luminal",".xlsx"))
write.xlsx(df_across[[2]]$res, file=paste0(result_dir,"Suppl.Tbl.09 Enrichment_Across_Tissue",".xlsx"))

@@

write.xlsx(df_pairwise[[1]]$value, file=paste0(result_dir,"Suppl.Tbl.06 Enrichment_Pairwise_Luminal",".xlsx"))
write.xlsx(df_pairwise[[2]]$value, file=paste0(result_dir,"Suppl.Tbl.10 Enrichment_Pairwise_Tissue",".xlsx"))
```

```{r TF PPI Analysis function, include=FALSE}
# filename <- DEG_files[1]
# gr_name <- gr_name[1]
# outfile <- enrichR_files[1]
TF_PPI_analysis.fun <- function(result_dir, filename, gr_name, outfile) {
  # Get DEG's files and filter p-value < 0.01
  sheets <- excel_sheets(paste0(result_dir, filename)) %>% set_names(.) %>% .[-c(1:2)]
  detables <- map(sheets, ~read_xlsx(paste0(result_dir, filename), sheet = .x, col_names = TRUE)) %>%
    map(.,~mutate(.x, DE = ifelse(.x$PValue > dge_cutoff , 0, ifelse(.x$logFC < 0, -1, 1 )))) %>% 
    map(.,~filter(., .$PValue <= 0.01))

@@

        }else{if(length(save_f) == 0){save_f <- append(save_f, f_n)} }
      }
      l <- bind_rows(save_f, .id = "Regulation") %>%
        filter(Adjusted.P.value <= 0.05)
      l <- set_names(list(l), paste0(i))
      save_l <- append(save_l, l ) 
    } 
    write.xlsx(save_l, file=paste0(result_dir, outfile), row.names=FALSE)
  }
```

```{r TF PPI Analysis, eval=FALSE, include=FALSE}
TF_PPI_analysis.fun(result_dir, DEG_files[1], gr_name[1], enrichR_files[1]) # writes Suppl.Tbl.07
TF_PPI_analysis.fun(result_dir, DEG_files[2], gr_name[2], enrichR_files[2]) # writes Suppl.Tbl.11
```

@@

    f_DOWN <- read_xlsx(paste0(result_dir, file), sheet = x) %>% filter(Regulation == "down")
    f_UP <- read_xlsx(paste0(result_dir, file), sheet = x) %>% filter(Regulation == "up")

@@

sheets <- excel_sheets(paste0(result_dir, DEG_files[1])) %>% set_names(.) %>% .[-c(1:2)]
arrange_plots.fun(enrich_L, "Luminal_gr", "Luminal", sheets, "TF_PPI_enrichment", enrichR_files[1], Layout = l)

@@

```{r Figure 5, message=FALSE, warning=FALSE, echo=FALSE, fig.height=6, crop = TRUE}
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)
# Layout
l <- list(mat = matrix(c(1,2,3,4,4,4,5,5,5,
                         1,2,3,4,4,4,5,5,5,
                         6,6,6,7,7,8,8,9,9,
                         10,10,10,11,11,12,12,13,13),
                nrow = 3,ncol = 9,byrow = T),
          widths = c(1.14,3.5,.36,2.5,2.5,2.5,2.5,2.5,2.5),
          heigth = c(1,1,1.5)
          )

sheets <- excel_sheets(paste0(result_dir, DEG_files[2])) %>% set_names(.) %>% .[-c(1:2)]
arrange_plots.fun(enrich_T, "Tissue_gr", "Tissue", sheets, "TF_PPI_enrichment", enrichR_files[2], Layout = l)

@@

pages <- list(list("DEGs L2T2 vs L2T3"=t), df_across[[1]]$res) %>% flatten()
write.xlsx(pages, file=paste0(result_dir,"Suppl.Tbl.12 L2T2_L2T3_DEGs_and_enrichment.xlsx")) 
```

## igraph network plot
```{r igraph network, eval=FALSE, warning=FALSE, include=FALSE}
# 1. Change the groups of interest by assigning condition_use
# 2. Change the number of genes to be included in the network by changing n
#    look at tempD_i and tempU_i to see how many genes was significant
# 3. Adjust the size of the gene nodes and text in the graph by changing; square, circle and txt

# combinations
sheets <- map(DEG_files, ~excel_sheets(paste0(result_dir, .x))[-c(1:2)] ) %>%
  map(., ~set_names(.x))

@@

# Save all combination plots in one file
save_pdf.fun <- function(i, gr_name, comp){
  temp_i_name <- grep(i,list.files(paste0(result_dir),full.names=F),value=T)
  p <- map(comp, ~read_xlsx(paste0(result_dir, temp_i_name), sheet = .x))

@@

  par(mar = c(0, 0, .7, 0))  #bottom, left, top, right
  pdf(file = paste0(result_dir, "Plots/", i, "_network_",".pdf", sep=""))
    p <- imap(obj_igraph,
         ~with(.x, 
                 plot.igraph(g, label=V(g), page = T,
                 main = paste0(str_replace(.y, "_", " ")," regulated genes"),
                 layout=layout_with_kk(g), vertex.label.color="black" ,
                 vertex.size=v_size, vertex.label.cex=txt, vertex.label.font=2, 
                 vertex.shape=v_shape, vertex.color=v_color, marigin = c(-1,-4,0,0),
                 vertex.frame.color="grey60", curved=F)

@@

# if(isFALSE(dir.exists(paste0(result_dir,"")))){dir.create(paste0("../",result.dir),recursive = TRUE)}
# save_pdf.fun("TF_PPI_Luminal", "Luminal", comp = sheets[[1]])
# save_pdf.fun("TF_PPI_Tissue", "Tissue", comp = sheets[[2]])
